When does VPD drive or reduce ET?

### 2017-10-26 doc/eee_symposium/vpd.tex
reorganized to share figures for presentations

\usepackage[english]{babel}
 % \usepackage[utf8x]{inputenc}
\usepackage[style=authoryear]{biblatex}
\addbibresource{references.bib}
\usepackage{tikz}

\title[Your Short Title]{When does VPD drive or reduce ET?}
\author{Adam Massmann,  Pierre Gentine and Changjie Lin}
\institute{EEE Graduate Student Symposium}
\date{October 27th, 2017}

@@

\begin{frame}
  \[\frac{g_{a} \rho}{R* R_{air} \sigma uWUE \left(g_{1} + 1.0 \sqrt{- e_{s} \left(RH - 1.0\right)}\right)^{2} \left(\gamma + \frac{d}{d T} e_{s}\right)} \left(RH - 1.0\right) \left(- R* c_{p} \sigma uWUE \left(g_{1} + 1.0 \sqrt{- e_{s} \left(RH - 1.0\right)}\right)^{2} + 0.3125 R_{air} c_{s} g_{1} \gamma + 0.3125 R_{air} c_{s} \gamma \left(g_{1} + 1.0 \sqrt{- e_{s} \left(RH - 1.0\right)}\right)\right)\]
\end{frame}

>>>>

\usepackage[english]{babel}
 % \usepackage[utf8x]{inputenc}
\usepackage[style=authoryear]{biblatex}
\addbibresource{references.bib}
\usepackage{tikz}
\graphicspath{{figures/}}
\title[Your Short Title]{When does VPD drive or reduce ET?}
\author{Adam Massmann,  Pierre Gentine and Changjie Lin}
\institute{EEE Graduate Student Symposium}
\date{October 27th, 2017}

@@
